---
title: "Integration of shiny.semantic with other packages"
author: "Appsilon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
runtime: shiny
vignette: >
  %\VignetteIndexEntry{Integration of shiny.semantic with other packages}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
library(shiny)
library(shiny.semantic)
library(plotly)
library(leaflet)
```

## Integration with plotly or leaflet

Similarly to `shiny`, `shiny.semantic` works well with other popular R packages.
Let's see how to create a simple application with `plotly`.

```{r echo=T, include = T, eval = FALSE}
library(shiny)
library(shiny.semantic)
library(plotly)

ui <- semanticPage(
  segment(
    class = "basic",
    a(class="ui green ribbon label", "Plotly demo"),
    plotlyOutput("plot")

  )
)

server <- function(input, output, session) {
  output$plot <- renderPlotly({
    plot_ly(economics, x = ~date, color = I("black")) %>%
      add_lines(y = ~uempmed) %>%
      add_lines(y = ~psavert, color = I("red"))
  })
}

shinyApp(ui = ui, server = server)

```
And now let's have a look at similar example, but with `leaflet`.

```{r echo=T, include = T, eval = FALSE}
library(shiny)
library(shiny.semantic)
library(leaflet)

ui <- semanticPage(
  segment(
    class = "basic",
    a(class="ui blue ribbon label", "Leaflet demo"),
    leafletOutput("map")

  )
)

server <- function(input, output, session) {
  output$map <- renderLeaflet({
    m <- leaflet() %>% addTiles()
    m <- m %>% setView(21.00, 52.21, zoom = 12)
    m
  })
}

shinyApp(ui = ui, server = server)
```



## [Advanced] Using Fomantic UI JavaScript elements

Some Fomantic UI elements require to run a specific JS code when DOM document is ready. There are at least 2 options to do this:

1) Use `shinyjs`

```r
library(shinyjs)
...
jsCode <- " # Fomantic UI componts JS "
...
ui <- function() {
  shinyUI(
    semanticPage(
      title = "Your page title",
      shinyjs::useShinyjs(),
      # Your UI code
    )
  )
}
server <- shinyServer(function(input, output) {
  runjs(jsCode)
  # Your Shiny logic
})
shinyApp(ui = ui(), server = server)
```

2) Use `shiny::tags$script()`

```r
...
jsCode <- "
$(document).ready(function() {
  # Semantic UI components JS code, like:
  #$('.rating').rating('setting', 'clearable', true);
  #$('.disabled .rating').rating('disable');
})
...
"

ui <- function() {
  shinyUI(
    semanticPage(
      title = "My page",
      tags$script(jsCode),
      # Your UI code
    )
  )
}
...
server <- shinyServer(function(input, output) {
  # Your Shiny logic
})

shinyApp(ui = ui(), server = server)
```
